---
title: "Business Intelligence Project"
author: "korn"
date: "5/11/23"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: 72
---

# Student Details

+--------------------------------+---------------------------+
| **Student ID Numbers and Names | 1.  134644 - C -          |
| of Group Members**             |     Sebastian Muramara    |
|                                |                           |
|                                | 2.  136675 - C - Bernard  |
|                                |     Otieno                |
|                                |                           |
|                                | 3.  131589 - C - Agnes    |
|                                |     Anyango               |
|                                |                           |
|                                | 4.  131582 - C - Njeri    |
|                                |     Njuguna               |
|                                |                           |
|                                | 5.  136009 - C- Sera      |
|                                |     Ndabari               |
+--------------------------------+---------------------------+
| **GitHub Classroom Group       | Korn                      |
| Name**                         |                           |
+--------------------------------+---------------------------+
| **Course Code**                | BBT4206                   |
+--------------------------------+---------------------------+
| **Course Name**                | Business Intelligence II  |
+--------------------------------+---------------------------+
| **Program**                    | Bachelor of Business      |
|                                | Information Technology    |
+--------------------------------+---------------------------+
| **Semester Duration**          | 21^st^ August 2023 to     |
|                                | 28^th^ November 2023      |
+--------------------------------+---------------------------+

# Setup Chunk

**Note:** the following KnitR options have been set as the global
defaults: <BR>
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy = TRUE)`.

More KnitR options are documented here
<https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and
here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = FALSE
)

```
#  Lab 8.: Model Performance Comparison

## STEP 1. Install and Load the Required Packages
```{r STEP 1}
## mlbench ----
if (require("mlbench")) {
  require("mlbench")
} else {
  install.packages("mlbench", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## caret ----
if (require("caret")) {
  require("caret")
} else {
  install.packages("caret", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## kernlab ----
if (require("kernlab")) {
  require("kernlab")
} else {
  install.packages("kernlab", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## randomForest ----
if (require("randomForest")) {
  require("randomForest")
} else {
  install.packages("randomForest", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
```

## STEP 2. Load the Dataset
```{r  STEP 2}
data(Glass)

```
## STEP 3. The Resamples Function
```{r}

train_control <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

### LDA ----
set.seed(7)
diabetes_model_lda <- train(Type ~ ., data = Glass,
                            method = "lda", trControl = train_control)

### CART ----
set.seed(7)
diabetes_model_cart <- train(Type ~ ., data = Glass,
                             method = "rpart", trControl = train_control)

### KNN ----
set.seed(7)
diabetes_model_knn <- train(Type ~ ., data = Glass,
                            method = "knn", trControl = train_control)

### SVM ----
set.seed(7)
diabetes_model_svm <- train(Type ~ ., data = Glass,
                            method = "svmRadial", trControl = train_control)

### Random Forest ----
set.seed(7)
diabetes_model_rf <- train(Type ~ ., data = Glass,
                           method = "rf", trControl = train_control)

```
### 3.b. Call the `resamples` Function ----
```{r 3b}
results <- resamples(list(LDA = diabetes_model_lda, CART = diabetes_model_cart,
                          KNN = diabetes_model_knn, SVM = diabetes_model_svm,
                          RF = diabetes_model_rf))

```

## STEP 4. Display the Results
```{r  STEP 4}
## 1. Table Summary ----
summary(results)

## 2. Box and Whisker Plot ----

scales <- list(x = list(relation = "free"), y = list(relation = "free"))
bwplot(results, scales = scales)

## 3. Dot Plots ----

scales <- list(x = list(relation = "free"), y = list(relation = "free"))
dotplot(results, scales = scales)

## 4. Scatter Plot Matrix ----
splom(results)



# xyplot plots to compare models
xyplot(results, models = c("LDA", "CART"))

# or
# xyplot plots to compare models
xyplot(results, models = c("SVM", "LDA"))


## 6. Statistical Significance Tests ----

diffs <- diff(results)

summary(diffs)


```

